Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-02-06 man/figures/resilience_metrics.Rmd
update figures
reduce fig size
update figures and chronos
update legend

**Figure 7.** Response *Q. pyrenaica* forests to drought in terms of resistance, recovery and resilience of greenness (EVI; left-plots) and tree radial growth (BAI; right-plots) for the years 2005 and 2012. For EVI we compared northern populations (*black fill circle*) with southern ones (*blue empty circle*). For BAI we compared northern population (San Juan, SJ; *black triangle*) with southerns populations: Cáñar-High (CA-High; *blue empty squares*) and Cáñar-Low (CA-Low; *blue fill squares*). Different letters above error bars indicate significant *post hoc* differences between groups (see material and methods).

```{r plot_out, fig.height=6.5, dpi = 300, out.width = 0.8} 
grid_arrange_shared_legend(rt, rc, rs, ncol = 1, nrow = 3, position ='top')

>>>>

**Figure 7.** Response *Q. pyrenaica* forests to drought in terms of resistance, recovery and resilience of greenness (EVI; left-plots) and tree growth (BAI; right-plots) for the years 2005 and 2012. For EVI we compared northern populations (*black fill circle*) with southern ones (*blue empty circle*). For BAI we compared the northern population (San Juan, SJ; *black triangle*) with the two southerns populations: Cáñar-High (CA-High; *blue empty squares*) and Cáñar-Low (CA-Low; *blue fill squares*). Different letters above error bars indicate significant *post hoc* differences between groups (see material and methods).

```{r plot_out, fig.height=5, dpi = 300, out.width = 0.8} 
grid_arrange_shared_legend(rt, rc, rs, ncol = 1, nrow = 3, position ='top')
